---
title: "Data Overview"
author: "Runan Yao"
date: "February 21, 2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

```{r echo=FALSE}
source('Libraries.R')
#detach("package:RMySQL", unload=TRUE)
```

```{r echo=FALSE}
# Load Data
setwd("C:/GitRepo/Profile")
data <- read.csv("data08.csv.gz")
```

# Summarize
```{r echo=FALSE,results="hide"}
distinctId <- sqldf("SELECT DISTINCT id FROM data")
```
we have `r count(data)` weight records from `r count(distinctId)` user.

# Data Missing/Incorrect Analyze
##1. Brithday
```{r echo=FALSE}
#all <- sqldf("SELECT DISTINCT id FROM data")
tmp1 <- sqldf("SELECT DISTINCT id FROM data WHERE birthdate < '1918-01-01' or birthdate > '2018-01-01'")
```
`r count(tmp1)/count(distinctId)`% of user have incorrect brithdate.

Can a normal user register the account/membership without having a reasonable brithday?

        If yes, how we deal with their brithdate data? (default value? NULL?)
        
        If no, why we have so many incorrect brithdate data in DB.
```{r echo=FALSE}
rm(tmp1)
```

##2. Gender
```{r echo=FALSE}
tmp1 <- sqldf("SELECT DISTINCT id FROM data WHERE ( gender is not 'male' or gender is not 'female' )")
tmp2 <- sqldf("SELECT DISTINCT id FROM data WHERE gender is 'male'")
tmp3 <- sqldf("SELECT DISTINCT id FROM data WHERE gender is 'female'")
tmp4 <- sqldf("SELECT id FROM tmp1 WHERE ( id not in tmp2 and id not in tmp3 )")
tmp5 <- sqldf("SELECT id FROM tmp2 WHERE id in tmp3")
```
`r count(tmp4)/count(distinctId)`% of user has no gender data. `r count(tmp5)/count(distinctId)`% of user have both male and female show in data base.

```{r}
rm(tmp1, tmp2, tmp3, tmp4, tmp5)
```


##3. First Weight
```{r echo=FALSE}
tmp1 <- sqldf("SELECT DISTINCT id FROM data WHERE ( first_weight < 10 or first_weight > 500 )") # incorrect first weight records
tmp2 <- sqldf("SELECT DISTINCT id FROM data WHERE ( first_weight > 10 and first_weight < 500 )") # correct first weight records
tmp3 <- sqldf("SELECT id FROM tmp1 WHERE id not in tmp2")

```
`r count(tmp3)/count(distinctId)`% of user have incorrect first weight.
Great. Each user has at least one record with first weight in.
```{r echo=FALSE}
rm(tmp1, tmp2, tmp3)
```

##4. Expected Weight
```{r echo=TRUE}
tmp1 <- sqldf("SELECT id,first_weight, goal_weight, (first_weight - goal_weight) as expected_weight_loss FROM data WHERE goal_weight > 10 and goal_weight < 500 and first_weight >= goal_weight GROUP BY id ")
max(tmp1$goal_weight)
min(tmp1$goal_weight)
hist(tmp1$goal_weight,  breaks = seq(0,500, by = 10))
hist(tmp1$expected_weight_loss , breaks = seq(0, 500, by = 10))
```

`r (count(distinctId) - count(tmp1))/count(distinctId)`% of user have incorrect goal weight or first weight.


Some of the goal weight data is not reasonable. Do we have any requirement on the 'goal weight' when member join into the program?
        
##5. Weight record
```{r echo=FALSE}
tmp2 <- sqldf("SELECT count(*) FROM data WHERE dates > '1918-01-01' and dates < '2018-01-01'")
```
`r tmp2/count(data)`% of records contains weight data.

MISSING COMMENT HERE.






