---
title: "Data Overview"
author: "Runan Yao"
date: "February 21, 2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

```{r echo=FALSE}
source('Libraries.R')
#detach("package:RMySQL", unload=TRUE)
```

```{r echo=FALSE}
# Load Data
setwd("C:/GitRepo/Profile")
data <- read.csv("data08.csv.gz")
```

# Summarize
```{r echo=FALSE,results="hide"}
distinctId <- sqldf("SELECT DISTINCT id FROM data")
```
we have `r count(data)` weight records from `r count(distinctId)` user.

# Data Missing/Incorrect Analyze
##1. Brithday
```{r echo=FALSE}
#all <- sqldf("SELECT DISTINCT id FROM data")
tmp1 <- sqldf("SELECT DISTINCT id FROM data WHERE birthdate < '1918-01-01' or birthdate > '2018-02-22'")
```
`r count(tmp1)/count(distinctId)`% of user have incorrect brithdate.

Can a normal user register the account/membership without having a reasonable brithday?

        If yes, how we deal with their brithdate data? (default value? NULL?)
        
        If no, why we have so many incorrect brithdate data in DB.
```{r echo=FALSE}
rm(tmp1)
```

##2. Gender
```{r echo=FALSE}
tmp1 <- sqldf("SELECT DISTINCT id FROM data WHERE ( gender is not 'male' or gender is not 'female' )")
tmp2 <- sqldf("SELECT DISTINCT id FROM data WHERE gender is 'male'")
tmp3 <- sqldf("SELECT DISTINCT id FROM data WHERE gender is 'female'")
tmp4 <- sqldf("SELECT id FROM tmp1 WHERE ( id not in tmp2 and id not in tmp3 )")
tmp5 <- sqldf("SELECT id FROM tmp2 WHERE id in tmp3")
```
`r count(tmp4)/count(distinctId)`% of user has no gender data. `r count(tmp5)/count(distinctId)`% of user have both male and female show in data base.

```{r}
rm(tmp1, tmp2, tmp3, tmp4, tmp5)
```


##3. First Weight
```{r echo=FALSE}
tmp1 <- sqldf("SELECT DISTINCT id FROM data WHERE ( first_weight < 10 or first_weight > 500 )") # incorrect first weight records
tmp2 <- sqldf("SELECT DISTINCT id FROM data WHERE ( first_weight > 10 and first_weight < 500 )") # correct first weight records
tmp3 <- sqldf("SELECT id FROM tmp1 WHERE id not in tmp2")

```
`r count(tmp3)/count(distinctId)`% of user have incorrect first weight.

```{r echo=FALSE}
rm(tmp1, tmp2, tmp3)
```

##4. Expected Weight 
```{r echo=TRUE}
tmp1 <- sqldf("SELECT id,first_weight, goal_weight, (first_weight - goal_weight) as expected_weight_loss FROM data WHERE goal_weight > 10 and goal_weight < 500 and first_weight >= goal_weight GROUP BY id ")

max(tmp1$goal_weight)
min(tmp1$goal_weight)
hist(tmp1$goal_weight,  breaks = seq(0,500, by = 10))
hist(tmp1$expected_weight_loss , breaks = seq(0, 500, by = 10))


tmp2 <- sqldf("SELECT id,first_weight, goal_weight, (first_weight - goal_weight)/first_weight as expected_weight_loss_rate FROM data WHERE goal_weight > 10 and goal_weight < 500 and first_weight >= goal_weight GROUP BY id ")

hist(tmp2$expected_weight_loss_rate)


```

`r (count(distinctId) - count(tmp1))/count(distinctId)`% of user have incorrect goal weight or first weight.

```{r}
rm(tmp1)
```

Some of the goal weight data is not reasonable. Do we have any requirement on the 'goal weight' when member join into the program?
        
##5. Weight record
```{r echo=FALSE}
tmp1 <- sqldf("SELECT count(*) FROM data WHERE weight > 10 and weight < 1000")
tmpk <- sqldf("SELECT count(*) FROM data WHERE weight >= 1000")
tmpk2 <- sqldf("SELECT count(*) FROM data WHERE weight <= 10")
tmpk2 <- sqldf("SELECT count(*) FROM data WHERE weight * 1 = weight ")


u <- sqldf("SELECT weight FROM data")
notNum <- is.na( as.numeric(data$weight) )
sum(notNum)

```
`r tmp1/count(data)`% of records contains reasonable weight data.

1. We are using weight > 10 && weight < 500 to select correct data. Does this work? Is there any case member has weight higher than 500?

# 


## 
```{r}
# tmp1 <- sqldf("SELECT id,first_weight, goal_weight, (first_weight - goal_weight) as expected_weight_loss, (first_weight - weight)/3 as progress FROM data WHERE goal_weight > 10 and goal_weight < 500 and first_weight >= goal_weight and months = 3 ")
# 
# tmp2 <- sqldf("SELECT id,first_weight, goal_weight, (first_weight - goal_weight) as expected_weight_loss, (first_weight - weight)/6 as progress FROM data WHERE goal_weight > 10 and goal_weight < 500 and first_weight >= goal_weight and months = 6 ")
#  
# tmp3 <- sqldf("SELECT id,first_weight, goal_weight, (first_weight - goal_weight) as expected_weight_loss, (first_weight - weight)/9 as progress FROM data WHERE goal_weight > 10 and goal_weight < 500 and first_weight >= goal_weight and months = 9 ")
#  
# tmp4 <- sqldf("SELECT id,first_weight, goal_weight, (first_weight - goal_weight) as expected_weight_loss, (first_weight - weight)/12 as progress FROM data WHERE goal_weight > 10 and goal_weight < 500 and first_weight >= goal_weight and months = 12 ")

tmp1 <- sqldf("SELECT id, gender, max(months) as quit_month, min(weight) as best_weight, (first_weight - goal_weight) as expected_weight_loss FROM data WHERE goal_weight > 10 and goal_weight < 500 and first_weight >= goal_weight and weight > 10 and weight < 500 and (gender = 'male' or gender = 'female') GROUP BY id")
scatter.smooth(x=tmp1$expected_weight_loss, y=tmp1$quit_month)

tmp1$expected_weight_loss = cut( tmp1$expected_weight_loss, breaks = seq(0, 150, by = 10))
ggplot(tmp1, aes(y=tmp1$quit_month, x=tmp1$expected_weight_loss, fill = tmp1$gender), position = 'dodge')+geom_boxplot()


```


## Success rate
```{r}
tmp1 <- sqldf("SELECT id, gender, max(months) as quit_month, min(weight) <= goal_weight as success, (first_weight - goal_weight) as expected_weight_loss FROM data WHERE goal_weight > 10 and goal_weight < 500 and first_weight >= goal_weight and weight > 10 and weight < 500 and (gender = 'male' or gender = 'female') GROUP BY id")
sum(tmp1$success)/count(tmp1)

tmp2 <- sqldf("SELECT id, gender, max(months) as quit_month, min(weight) <= goal_weight * 1.1 as success, (first_weight - goal_weight) as expected_weight_loss FROM data WHERE goal_weight > 10 and goal_weight < 500 and first_weight >= goal_weight and weight > 10 and weight < 500 and (gender = 'male' or gender = 'female') GROUP BY id")
sum(tmp2$success)/count(tmp2)

tmp3 <- sqldf("SELECT id, gender, max(months) as quit_month, min(weight) <= first_weight * 0.9 as success, (first_weight - goal_weight) as expected_weight_loss FROM data WHERE goal_weight > 10 and goal_weight < 500 and first_weight >= goal_weight and weight > 10 and weight < 500 and (gender = 'male' or gender = 'female') GROUP BY id")
sum(tmp3$success)/count(tmp3)




```

## for people successfully reach their goal
```{r}

tmp4 <- sqldf("SELECT id, gender, min(months) as first_month_reach_goal, (first_weight - goal_weight) as expected_weight_loss, first_weight FROM data WHERE goal_weight > 10 and goal_weight < 500 and first_weight >= goal_weight and weight > 10 and weight < 500 and (gender = 'male' or gender = 'female') and weight <= goal_weight GROUP BY id")

hist(tmp4$first_month_reach_goal, breaks = seq(0, 55, by = 1) )

tmp5 <- sqldf("SELECT a.id, a.gender, a.quit_month, b.first_month_reach_goal, b.expected_weight_loss, b.first_weight FROM tmp1 a join tmp4 b on a.id = b.id")
scatter.smooth(x=tmp5$first_month_reach_goal, y=tmp5$quit_month)

ggplot(tmp5, aes(y=tmp5$quit_month, x=factor(tmp5$first_month_reach_goal)), position = 'dodge')+geom_boxplot()

hist(tmp5$quit_month - tmp5$first_month_reach_goal, breaks = seq(0, 55, by = 1))
k1 <- tmp5$quit_month
k2 <- tmp5$first_month_reach_goal
k3 <- k1 - k2
table(k3)
hist(k3, breaks = seq(0, 55, by = 1))
ggplot(tmp5, aes(y=tmp5$quit_month - tmp5$first_month_reach_goal, x=factor(tmp5$first_month_reach_goal)), position = 'dodge')+geom_boxplot()

ggplot(tmp5, aes(y=tmp5$quit_month - tmp5$first_month_reach_goal, x=factor(round_any(tmp5$expected_weight_loss, 10)), position = 'dodge'))+geom_boxplot()

ggplot(tmp5, aes(y=tmp5$quit_month - tmp5$first_month_reach_goal, x=factor(round_any(tmp5$first_weight,50)), position = 'dodge'))+geom_boxplot()

```